---
title       : Air Quality Map
subtitle    : Developing Data Products - Course Project
author      : Alexander Zhou
framework   : io2012        
highlighter : highlight.js  
hitheme     : solarized_dark      
widgets     : []           
mode        : selfcontained 
knit        : slidify::knit2slides
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(jsonlite)
require(curl) 
require(webshot)
```

<style> 
  .title-slide { background-color: #FFFFFF; }
</style>

## Background

The goal of this project was to develop a dynamic shiny application displaying the current Air Quality Index (AQI) for the current location. The index scale is not linear. Instruction of how to calculate the index can be found <a href='https://en.wikipedia.org/wiki/Air_quality_index#Computing_the_AQI'>here</a>. The AQI divides the air pollution into six levels

1. Good 
2. Moderate
3. Unhealthy for Sensitive Groups
4. Unhealthy
5. Very Unhealthy
6. Hazardous

Project links:
* <a href='https://github.com/haechi/DataProducts-Project'>Github repository</a>
* <a href='http://haechi.shinyapps.io/air_quality_map'>Shiny Application</a>

---
## Functionality

The application will determine the selected location and set a rectangle boundary around the approximate location. The sensor station data for station within the boundary is then pull as <a href='https://json.org'>JSON</a> object from the <a href='http://aqicn.org/'>World Air Quality Index</a> API. 

The sensor station data is then overlaid on the map. The marker color is changed accordingly  to the AQI level.

Additionally, the user has the following menu options
* Change the location by selecting a city from the drop-down list
* Displaying a short help text
* Hiding the legend

---
## JSON Querry 

For the data processing function the server will first assemble a formatted URL directed to the World Air Quality Index <a href='http://aqicn.org/api/'>API</a>. The API token was generated before on the API homepage. 
```{r json}
token <- "3e0dd90175924cf5dd95296e75f93e13f9dc1cb3"
id.loc <- "here"
url.loc <- paste("http://api.waqi.info/feed/",id.loc,"/?token=",token,sep="")
json.loc <- as.data.frame(fromJSON(url.loc))
json.loc$data.city.geo[]
```
The geo location obtained from this query is then used to again to obtain measurement stations in close proximity. The stations AQI level is determined and the resulting `dataframe` is passed to `leavelet` for rendering.

---
## Example Data Obtained from the API

The actual api data can be obtained by
```{r aqi}
json.loc$data.aqi[1]
```
The name of the name of the city from the approximated location 
```{r plot}
json.loc$data.city.name[1]
```